---
title: "Actor Analysis"
author: "Evelyn Salas"
date: "2/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("analysis.R")
actor_name <- "Brad Pitt"
```

Data analysis about some of my favorite movie actors!

## Trending Actors

Here are the top five actors trending during the week of `r as.Date("2020-02-13")-7`!

```{r trending_actors, echo=FALSE}

library(knitr)
get_trending_table("person", "week") %>% 
  kable()

actor_info <- 
get_actor_data(actor_name)

imdbbase_uri <- "https://www.imdb.com/name/"

actor_imdblink <- paste0(imdbbase_uri, actor_info$imdb_id)

```

## `r actor_name`

`r actor_name` (`r actor_imdblink`) was on the trending list this week. This is for good reason too. `r actor_name` has an impressive repertoire:

```{r movie_titles, echo=FALSE}
md_list_titles <-
paste("-", actor_info$title, collapse = "\n")

```

`r md_list_titles`

```{r specific_actor, echo=FALSE}



Bio <- 
paste(actor_info$biography) 



```

##### Biography

`r Bio`

### `r actor_name`'s Popularity Over the Years




```{r actor_analysis, echo=FALSE}
actor_analysis <- 
analyze_actor("Brad Pitt") 

Year_and_Popularity <- 
actor_analysis[[3]] %>%  kable()


```

`r Year_and_Popularity`

```{r peak, echo=FALSE}
peak <- 
actor_analysis[[2]]

peak_year <- 
peak$year

```

As I was making this report, I wondered when `r actor_name` had peaked in popularity. To answer this question, I grouped their movies by year and then calculated the average rating for their movies each year. I was surpried to find out that `r actor_name` was most popular in `r peak_year`!



##### Raw Data

```{r raw_data, echo=FALSE}

actor_analysis[[1]] %>% kable()

```
